---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# primerspe

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/primerspe)](https://CRAN.R-project.org/package=primerspe)
<!-- badges: end -->

The goal of primerspe is to have a local replicate of Rstudio primers. The original material was translated to Spanish for educational purposes.

## Installation

You can install the developmental version of `primerspe` with:

<!-- You can install the released version of primerspe from [CRAN](https://CRAN.R-project.org) with: -->

``` r
if(!require("remotes")) install.packages("remotes")
remotes::install_github("avallecam/primerspe")
```

También puedes instalarlo descargando el archivo `.tar.gz` o `.zip` (este sólo funciona en Windows) e instalar el paquete `primerspe` desde la opción __Tools -> Install Packages -> Install from -> Package Archive File (.zip; .tar.gz)__.

## `learnr` tutorial

```{r example, eval=FALSE,echo=TRUE}
# instalar learner
if(!require("learnr")) install.packages("learnr")

# correr tutorial 01
learnr::run_tutorial(name = "04-programacion-basica",package = "primerspe")

# correr tutorial 02
learnr::run_tutorial(name = "funciones-tutorial",package = "primerspe")
```

Si tienes la última versión de RStudio aparecerá en tu panel de __Tutorial__. Sino, se abriá en tu buscador web.

## Referencias

- Rstudio Primers https://rstudio.cloud/learn/primers
- Taller MetaDocencia LatinR Rladies https://github.com/yabellini/curso_learnr
- Generando tutoriales interactivos https://yabellini.netlify.app/es/post/tutorialesconlearnr/
- Empaquetando tutoriales interactivos https://yabellini.netlify.app/es/post/empaquetandotutoriales/
- RECON Learn tutorials in Spanish https://www.reconlearn.org/topics/spanish.html
